Kamala Harris Rises as the 2024 Election Front Runner: A Poll-of-Polls Forecast

### 2024-10-24 paper/paper.qmd
R package reference & graph/table caption updates

In performing the analysis, we utilized several R packages. @tidyverse was used for data manipulation and visualization and @rstanarm, @modelsummary was respectively used for Bayesian modeling and generating model summaries. For visualizing results, @ggplot2 was used and @kableExtra helped format tables for presentation. These packages provided a framework for efficient data processing, modeling, and reporting.

@@

```{r}
#| label: tbl-pctraw1
#| tbl-cap: Summary Statistics for the 'pct' Variable (Raw Data)
#| echo: false

# Calculate summary statistics for the 'pct' variable
summary_stats <- raw_elections_data %>%
  summarize(
    mean = mean(pct, na.rm = TRUE),
    median = median(pct, na.rm = TRUE),
    min = min(pct, na.rm = TRUE),
    max = max(pct, na.rm = TRUE),
    sd = sd(pct, na.rm = TRUE),
    n = n()
  )

@@

```
```{r}
#| label: fig-pct2
#| fig-cap: Distribution of the 'pct' Variable (Raw Data)
#| echo: false

@@

```
```{r}
#| label: tbl-pctfilter1
#| tbl-cap: Summary Statistics for the 'pct' Variable (Filtered Data)
#| echo: false

# Calculate summary statistics for the 'pct' variable
summary_stats <- harris_data %>%
  summarize(
    mean = mean(pct, na.rm = TRUE),
    median = median(pct, na.rm = TRUE),
    min = min(pct, na.rm = TRUE),
    max = max(pct, na.rm = TRUE),
    sd = sd(pct, na.rm = TRUE),
    n = n()
  )

@@

```
```{r}
#| label: fig-pctfilter2
#| fig-cap: Distribution of the 'pct' Variable (Filtered Data)
#| echo: false

@@

```{r}
#| label: tbl-date
#| tbl-cap: Summary Statistics for the 'end_date' Variable (Raw Data)
#| echo: false

@@

```
```{r}
#| label: fig-date
#| fig-cap: Distribution of the 'end_date' Variable (Raw Data)
#| echo: false

@@

```{r}
#| label: tbl-date2
#| tbl-cap: Summary Statistics for the 'end_date' Variable (Filtered Data)
#| echo: false

@@

```{r}
#| label: fig-date2
#| fig-cap: Distribution of the 'end_date' Variable (Filtered Data)
#| echo: false

@@

```{r}
#| label: tbl-predictors1
#| tbl-cap: Number of Distinct Values for the 'pollster', 'state' Variable (Raw Data)
#| echo: false

@@

```{r}
#| label: tbl-predictors2
#| tbl-cap: Number of Distinct Values for the 'pollster', 'state' Variable (Filtered Data)
#| echo: false

@@

```{r}
#| label: fig-pollster
#| fig-cap: Distribution of the 'pollster' Variable (Filtered Data for Harris)
#| echo: false

@@

```{r}
#| label: fig-state
#| fig-cap: Distribution of the 'state' Variable (Filtered Data for Harris)
#| echo: false

@@

```{r}
#| label: tbl-pollscore
#| tbl-cap: Summary statistics for the 'pollscore' Variable (Raw Data)
#| echo: false

summary_stats <- raw_elections_data %>%
  summarize(
    mean = mean(pollscore, na.rm = TRUE),
    median = median(pollscore, na.rm = TRUE),
    min = min(pollscore, na.rm = TRUE),
    max = max(pollscore, na.rm = TRUE),
    sd = sd(pollscore, na.rm = TRUE),
    n = n()
  )

@@

```{r}
#| label: fig-pollscore
#| fig-cap: Distribution of the 'pollscore' Variable (Raw Data)
#| echo: false

# Distribution of 'pollscore' (bar plot)
ggplot(raw_elections_data, aes(x = factor(pollscore))) +
  geom_bar(fill = "skyblue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Pollscore",
       y = "Count")

@@

```{r}
#| label: tbl-pollscore2
#| tbl-cap: Summary statistics for the 'pollscore' Variable (Filtered Data)
#| echo: false

summary_stats <- harris_data %>%
  summarize(
    mean = mean(pollscore, na.rm = TRUE),
    median = median(pollscore, na.rm = TRUE),
    min = min(pollscore, na.rm = TRUE),
    max = max(pollscore, na.rm = TRUE),
    sd = sd(pollscore, na.rm = TRUE),
    n = n()
  )

@@

```{r}
#| label: fig-pollscore2
#| fig-cap: Distribution of the 'pollscore' Variable (Filtered Data)
#| echo: false

@@

::: {.layout}
## Image Row

>>>>

In performing the analysis, we utilized several R packages. `tidyverse` [@tidyverse] was used for data manipulation and visualization and `rstanarm` [@rstanarm], `modelsummary` [@modelsummary] was respectively used for Bayesian modeling and generating model summaries. For visualizing results, `ggplot2` [@ggplot2] was used and `kableExtra` [@kableExtra] helped format tables for presentation. These packages provided a framework for efficient data processing, modeling, and reporting.

@@

```{r}
#| label: tbl-pctraw1
#| tbl-cap: Summary statistics for the proportion(%) of support that candidates received in the poll
#| echo: false

# Calculate summary statistics for the 'pct' variable
summary_stats <- raw_elections_data %>%
  summarize(
    mean = round(mean(pct, na.rm = TRUE), 2),
    median = round(median(pct, na.rm = TRUE),2),
    min = round(min(pct, na.rm = TRUE), 2),
    max = round(max(pct, na.rm = TRUE), 2),
    sd = round(sd(pct, na.rm = TRUE), 2),
    n = n()
  )

@@

```
```{r}
#| label: fig-pct2
#| fig-cap: Distribution of the proportion(%) of support that candidates received in the poll
#| echo: false

@@

```
```{r}
#| label: tbl-pctfilter1
#| tbl-cap: Summary statistics for the proportion(%) of support that Harris received in high-quality polls
#| echo: false

# Calculate summary statistics for the 'pct' variable
summary_stats <- harris_data %>%
  summarize(
    mean = round(mean(pct, na.rm = TRUE), 2),
    median = round(median(pct, na.rm = TRUE), 2),
    min = round(min(pct, na.rm = TRUE), 2),
    max = round(max(pct, na.rm = TRUE), 2),
    sd = round(sd(pct, na.rm = TRUE), 2),
    n = n()
  )

@@

```
```{r}
#| label: fig-pctfilter2
#| fig-cap: Distribution of the proportion(%) of support that Harris received in high-quality polls
#| echo: false

@@

```{r}
#| label: tbl-date
#| tbl-cap: Summary statistics for the date the poll was concluded
#| echo: false

@@

```
```{r}
#| label: fig-date
#| fig-cap: Distribution of the date the poll was concluded
#| echo: false

@@

```{r}
#| label: tbl-date2
#| tbl-cap: Summary statistics for the date the high-quality polls for Harris was concluded
#| echo: false

@@

```{r}
#| label: fig-date2
#| fig-cap: Distribution of the date the high-quality polls for Harris was concluded
#| echo: false

@@

```{r}
#| label: tbl-predictors1
#| tbl-cap: Number of distinct polling organizations and US states where the poll was conducted
#| echo: false

@@

```{r}
#| label: tbl-predictors2
#| tbl-cap: Number of distinct high-quality polling organizations and US states where more than 60 polls for Harris were conducted
#| echo: false

@@

```{r}
#| label: fig-pollster
#| fig-cap: Distribution of polling organizations where high-quality polls for Harris were conducted
#| echo: false

@@

```{r}
#| label: fig-state
#| fig-cap: Distribution of US states where the more than 60 polls for Harris were conducted
#| echo: false

@@

```{r}
#| label: tbl-pollscore
#| tbl-cap: Summary statistics for the reliability scores of pollsters
#| echo: false

summary_stats <- raw_elections_data %>%
  summarize(
    mean = round(mean(pollscore, na.rm = TRUE),2),
    median = round(median(pollscore, na.rm = TRUE),2),
    min = round(min(pollscore, na.rm = TRUE),2),
    max = round(max(pollscore, na.rm = TRUE),2),
    sd = round(sd(pollscore, na.rm = TRUE),2),
    n = n()
  )

@@

```{r}
#| label: fig-pollscore
#| fig-cap: Distribution of the reliability scores of pollsters
#| echo: false

# Distribution of 'pollscore' (bar plot) with simplified x-axis labels
ggplot(raw_elections_data, aes(x = factor(pollscore))) +
  geom_bar(fill = "skyblue", alpha = 0.7, color = "black") +
  theme_minimal() +
  scale_x_discrete(breaks = c(-1.5, -1, -0.5, 0, 0.5, 1, 1.5)) +  # Simplified labels at 0.5 intervals
  labs(x = "Pollscore",
       y = "Count")

@@

```{r}
#| label: tbl-pollscore2
#| tbl-cap: Summary statistics for the reliability scores of high-quality pollsters used for analysis
#| echo: false

summary_stats <- harris_data %>%
  summarize(
    mean = round(mean(pollscore, na.rm = TRUE),2),
    median = round(median(pollscore, na.rm = TRUE),2),
    min = round(min(pollscore, na.rm = TRUE),2),
    max = round(max(pollscore, na.rm = TRUE),2),
    sd = round(sd(pollscore, na.rm = TRUE),2),
    n = n()
  )

@@

```{r}
#| label: fig-pollscore2
#| fig-cap: Distribution of the reliability scores of high-quality pollsters used for analysis
#| echo: false

@@

::: {.layout}
## Survey Demo
